Comparison of Fast Imaging Architectures for Large, Multi-scale, Hierarchical Aperture Arrays

### 2024-06-04 ms.tex
Update on Overleaf.

\begin{figure*}
\centering
\subfloat[][\texttt{LAMBDA-I} \label{fig:1D-coherent-compcost-LAMBDA-I}]
{\includegraphics[width=\textwidth]
{figures/1D_coherent_per_pixel_compcost_analysis_LAMBDA-I.pdf}
} \\
\subfloat[][\texttt{SKA1-Low-core} \label{fig:1D-coherent-compcost-LAMBDA-I}]
{\includegraphics[width=\textwidth]
{figures/1D_coherent_per_pixel_compcost_analysis_SKA1-low-core.pdf}
} \\
\subfloat[][\texttt{SKA1-Low} \label{fig:1D-coherent-compcost-LAMBDA-I}]
{\includegraphics[width=\textwidth]
{figures/1D_coherent_per_pixel_compcost_analysis_SKA1-low.pdf}
} 
\caption{(Top): One-dimensional slices of the computational cost for coherent-incoherent imaging using station-level voltage beamforming for \texttt{SKA-low-core}, \texttt{SKA-low}, and \texttt{LAMBDA-I}. (Middle): Same for \texttt{CASPA}. (Bottom): Same for \texttt{FarView}. \label{fig:1D-incoherent-compcost-a}}
\end{figure*}

\begin{figure*}\ContinuedFloat
\subfloat[][\texttt{CASPA} \label{fig:1D-coherent-compcost-CASPA}]
{\includegraphics[width=\textwidth]
{figures/1D_coherent_per_pixel_compcost_analysis_CASPA.pdf}
} \\
\subfloat[][\texttt{FarView} \label{fig:1D-coherent-compcost-FarView}]
{\includegraphics[width=\textwidth]
{figures/1D_coherent_per_pixel_compcost_analysis_FarView.pdf}
}
\caption{Contd. (Top): One-dimensional slices of the computational cost for coherent-incoherent imaging using station-level voltage beamforming for \texttt{SKA-low-core}, \texttt{SKA-low}, and \texttt{LAMBDA-I}. (Middle): Same for \texttt{CASPA}. (Bottom): Same for \texttt{FarView}. \label{fig:1D-incoherent-compcost}}
\end{figure*}

>>>>

\begin{figure*}
\centering
\subfloat[][\texttt{LAMBDA-I} \label{fig:1D-coherent-compcost-LAMBDA-I}]
{\includegraphics[width=\textwidth]
{figures/1D_coherent_per_pixel_compcost_analysis_LAMBDA-I.pdf}
} \\
\subfloat[][\texttt{SKA1-Low-core} \label{fig:1D-coherent-compcost-LAMBDA-I}]
{\includegraphics[width=\textwidth]
{figures/1D_coherent_per_pixel_compcost_analysis_SKA1-low-core.pdf}
} \\
\subfloat[][\texttt{SKA1-Low} \label{fig:1D-coherent-compcost-LAMBDA-I}]
{\includegraphics[width=\textwidth]
{figures/1D_coherent_per_pixel_compcost_analysis_SKA1-low.pdf}
} 
\caption{One-dimensional slices of the computational cost density for (a) \texttt{LAMBDA-I}, (b) \texttt{SKA-low-core}, and (c) \texttt{SKA-low} using  coherent imaging at intra- and inter-station levels via VBF (gray) and EPIC (black) for intra-station processing, and VBF (dotted), EPIC (solid), XBF (dashed), and XFFT (dot-dashed) for inter-station processing of data from either of the strategies for intra-station processing. \label{fig:1D-incoherent-compcost-a}}
\end{figure*}

\begin{figure*}\ContinuedFloat
\subfloat[][\texttt{CASPA} \label{fig:1D-coherent-compcost-CASPA}]
{\includegraphics[width=\textwidth]
{figures/1D_coherent_per_pixel_compcost_analysis_CASPA.pdf}
} \\
\subfloat[][\texttt{FarView} \label{fig:1D-coherent-compcost-FarView}]
{\includegraphics[width=\textwidth]
{figures/1D_coherent_per_pixel_compcost_analysis_FarView.pdf}
}
\caption{Contd. Same as above but for (d) \texttt{CASPA}, and (e) \texttt{FarView} \label{fig:1D-incoherent-compcost}}
\end{figure*}
